Review of Group 8 by Group 1

### 2015-02-16 rmtw/a3/latex8.tex
Minor changes to the purpose

CM on the other hand could be seen as an umbrella for many theories and strategies. Such an example of this is the concept of innovation values fit by [CITE].

@@

\Section{Purpose of the Study}
It's an exploratory study. We want to find out how CM is done in such environemnts, if it's successful and how it can be improved.

>>>>

CM on the other hand could be seen as an umbrella for a plethora of theories and strategies. An example of a theory is the concept of innovation values fit by [CITE].

@@

\Section{Purpose of the Study}
The purpose of this study is to explore how changes to software processes are incorporated into a company where differing development paradigms are used. This exploratory study will take place at a large and successful telecommunications company. Much of the qualitative data will originate from current employees via a series of interviews. While the study will only take place at a single location, it will be conducted in such a way that it is applicable to any company willing to partake.
